Self Regulation Ontology Retest Analyses

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem prep

@@

```{r}
rel_comp %>% 
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  geom_point(alpha = 0.2)+
  theme(legend.title = element_blank())+
  xlab("Sample Size")+
  ylab("Retest reliability")

@@

```{r}
tmp = comp_lit_pred_out %>%
  select(-.n) %>%
  gather(key, value) %>%
  separate(key, c("stat", "sample"), sep = "_")

tmp$stat = as.factor(tmp$stat)
levels(tmp$stat) <- c("coefficient", expression(r^"2"))

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_discrete(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Prediction")+
  xlab('')+
  ylab('')

ggsave('Lit_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 10, height = 4, units = "in", limitsize = FALSE, dpi = 100)
```

>>>>

ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
ggplotly(rel_comp %>% 
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  geom_point(alpha = 0.2)+
  theme(legend.title = element_blank())+
  xlab("Sample Size")+
  ylab("Retest reliability"))

@@

```{r}
tmp = comp_lit_pred_out %>%
  select(-.n, -m_lit, -m_boot) %>%
  gather(key, value) %>%
  separate(key, c("stat", "sample"), sep = "_")

# tmp$stat = as.factor(tmp$stat)
# levels(tmp$stat) <- c("coefficient", expression(r^"2"))

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("white", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)

ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("purple", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)

ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
```
